---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `prodente`: **Pro**tein **De**terminants **En**richment **Tes**ting for UK Biobak Study Characteristics

<!-- badges: start -->
<!-- badges: end -->

The goal of `prodente` is to make results from an upcoming publication immediately accessible and useful.


## Installation

You can install the development version of `prodente` directly from GitHub:

```{r, eval=FALSE}
library(remotes)
install_github("comp-med/prodente")
```

## Getting Started

The API consists only of a hand-full of functions that mostly make working with the results table more convenient. Each important results object is immediately available as accessible data. 

```{r, eval=FALSE}
library(prodente)

```


```{r, eval=FALSE}
data(protein_mapping_table)
data(participant_characteristics_labels)
```

## Example

```{r, eval=FALSE}

```

