---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `prodente`: **Pro**tein **D**eterminants **En**richment **Te**sting 

<!-- badges: start -->
<!-- badges: end -->

The goal of `prodente` is to make results from an upcoming publication
immediately accessible and useful. This package contains functions to easily
test a list of proteins for enrichment of UK Biobank study characteristics.

## Installation

You can install the development version of `prodente` directly from GitHub:

```{r, eval=FALSE}
library(remotes)
install_github("comp-med/prodente")
```

## Getting Started

The API consists only of a hand-full of functions that mostly make working with
the results table more convenient. Each important results object is immediately
available as accessible data.

```{r}
library(prodente)

# There is example data provided
fasting_study_results <- prodente::fasting_study_results

# It is important to check that protein identifiers of your data are available
# in the background data.
check_protein_overlap(fasting_study_results$protein_id, return_missing = TRUE)

# Make sure to check the provided mapping table in case you have missing
# proteins. Maybe they are in the data but formatted slightly differently.
# Additionally, the table provides Olink IDs and UniProt IDs to make matching 
# easier
head(prodente::protein_mapping_table)
```

Enrichment tests can be stratified by sex or genetic ancestry. Set the
`test_across` parameter of the function `enrich_protein_characteristics()` to do
so.

```{r}
# Run enrichment tests for a list of proteins
results <- enrich_protein_characteristics(
  protein_foreground = fasting_study_results[group == "day_1", protein_id], 
  factor_minimum_explained_variance = 0, 
  test_across = "sex",
  n_cores = 8
  )


head(results[pval < 0.05 & or > 5, .(population, label)])
```

Enrichment tests can also be performed across several groups. Use the function
`enrichment_test_across_groups()` for this.

```{r}
# When data for several groups is available, supply a names list to this function
group_data <- list(
  day_1 = fasting_study_results[group == "day_1", protein_id],
  day_2 = fasting_study_results[group == "day_2", protein_id],
  day_3 = fasting_study_results[group == "day_3", protein_id],
  day_10 = fasting_study_results[group == "day_10", protein_id]
)

group_results <- enrichment_test_across_groups(
  protein_foreground_list = group_data, 
  test_across = "sex", 
  n_cores = 8
)

# You can plot enrichment results for a single subgroup (within either `sex` or `ancestry`)
enrichment_plot <- plot_enrichment_results(
  group_results,
  plot_population = "All"
)
```

### Accessing the data

To access the data provided in the package, use the `prodente::<DATA_OBJECT>` notation.

```{r}
fasting_study_results <- prodente::fasting_study_results
participant_characteristics_labels <- prodente::participant_characteristics_labels
protein_mapping_table <- prodente::protein_mapping_table
variance_decomposition_background <- prodente::variance_decomposition_background
```


